---
title: "Task 1"
author: "Grace Bianchi"
date: "2023-03-16"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=TRUE, warning = FALSE, message = FALSE, echo = TRUE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(here)
library(sf)
library(tmap)

## read in the data
spill_data <- read_csv(here("data/Oil_Spill_Incident_Tracking_[ds394].csv"))


ca_counties_sf <- read_sf(here("data/ca_counties/CA_Counties_TIGER2016.shp")) %>% 
  janitor::clean_names()
# st_crs(ca_counties_sf) epsg 3857



```

## Overview

Summary of code and findings and data (n=3247)
The data are collected by OSPR Field Response Team members for Marine oil spills and by OSPR Inland Pollution Coordinators and Wardens for Inland incidents.


**Data source:** Oil Spill Incident Tracking data, from the California Department of Fish and Wildlife 


[Metadata source](https://www.arcgis.com/sharing/rest/content/items/7464e3d6f4924b50ad06e5a553d71086/info/metadata/metadata.xml?format=default&output=html).

## Interactive Exploratory Map

This is an interactive map showing the location of oil spill events in California.

```{r}
# Set the viewing mode to "interactive":
tmap_mode(mode = "view")

# Then make a map (with the polygon fill color updated by variable 'land_area', updating the color palette to "BuGn"), then add another shape layer for the sesbania records (added as dots):
tm_shape(ca_counties_sf) +
  tm_fill("aland", palette = "BuGn") +
  tm_shape(sesbania_sf) +
  tm_dots()

```


# Choropleth map

Make an exploratory interactive map in tmap showing the location of oil spill events included in the data.
Make a finalized static choropleth map in ggplot in which the fill color for each county depends on the count of inland oil spill events by county for the 2008 oil spill data
```{r}
ggplot()

```

## Summary



