---
title: "Task 1"
author: "Grace Bianchi"
date: "2023-03-16"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=TRUE, warning = FALSE, message = FALSE, echo = TRUE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(here)
library(sf)
library(tmap)

```


## Overview

This code uses explores and visualize oil spill data using an interactive map of spill locations and a static choropleth map of the number of spill events by county. The data was collected by OSPR Field Response Team members for Marine oil spills incidents (n=3247) in 2008.

**Data source:** Lampinen, M. (2020, Jan. 31). Oil Spill Incident Tracking [ds394]. Calif. Dept. of Fish and Wildlife. Biogeographic Information and Observation System (BIOS). Retrieved from https://gis.data.ca.gov/datasets/7464e3d6f4924b50ad06e5a553d71086_0/explore?location=37.191046%2C-118.647988%2C6.47. [Metadata source.](https://www.arcgis.com/sharing/rest/content/items/7464e3d6f4924b50ad06e5a553d71086/info/metadata/metadata.xml?format=default&output=html).


```{r}
## read in the data
spill_data <- read_csv(here("data/Oil_Spill_Incident_Tracking_[ds394].csv")) %>% 
  janitor::clean_names()

ca_counties_sf <- read_sf(here("data/ca_counties/CA_Counties_TIGER2016.shp")) %>% 
  janitor::clean_names() %>% 
  rename(county_name = name) 
# st_crs(ca_counties_sf) epsg 3857

# convert to spill observations to sf
spills_sf <- st_as_sf(spill_data, coords = c("x","y"), crs=st_crs(ca_counties_sf)) 
```


## Interactive Exploratory Map of California Oil Spills

This is an interactive map of the oil spill locations (n=3,237) across California in 2008. 

```{r fig.align="center"}
# Set the viewing mode to "interactive":
tmap_mode(mode = "view")

# Then make a map (with the polygon fill color updated by variable 'land_area', updating the color palette to "BuGn"), then add another shape layer for the sesbania records (added as dots):
tm_shape(spills_sf) +
  tm_dots(col = "specificlo", id="dateofinci", title = "Location Type") +
  tm_layout("Oil Spils in California in 2008")

```


# Choropleth map of Inland Oil Spills

There were 2,024 records of oil spills in inland California in 2008. Los Angeles County (n=340) and San Mateo County (n=173) had the greatest number of inland oil spill records. Modoc was the only county that did not report an oil spill in 2008. 

```{r}
# join spill data with county shp
county_spills_sf <- ca_counties_sf %>% 
  st_join(spills_sf)

# summarize observations for each county
spill_counts_inland <- county_spills_sf %>% 
  filter(inlandmari == "Inland") %>% 
  group_by(county_name) %>% 
  summarize(n_records = sum(!is.na(objectid))) # count by records in the data set

ggplot(data = spill_counts_inland) +
  geom_sf(aes(fill = n_records), color = "white", size = 0.1) +
  scale_fill_gradientn(colors = c("lightgray", "orange", "red")) +
  labs(fill = "Number of inland oil spill records") +
  theme_void()
```







