---
title: "Time Series Summary"
author: "Grace Bianchi"
date: "2023-03-19"
output: 
  html_document:
    code_folding: hide
    theme: cosmo
  
---

```{r setup, include=TRUE, message=FALSE, warning=TRUE, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=TRUE)

library(here)
library(tidyverse)
library(patchwork)
library(tsibble)
library(feasts)

```

##  tabs {.tabset}

### Summary

2 images

Sumary of data set 

This code explores adult fish passage records from 2001 to 2010 at the Willamette Falls fish ladder on the Willamette River (Oregon). Data were shared by and accessed from [Columbia River DART](https://www.cbr.washington.edu/dart/query/adult_graph_text) (Data Access in Real Time).


```{r}
fish_data <- read_csv(here("data/willamette_fish_passage.csv")) %>% 
  replace(is.na(.), 0) %>% # replace NA values with zero
   mutate(date = mdy(Date)) %>% 
  select("date", "Coho", "Jack Coho", "Steelhead", "TempC") %>% 
  as_tsibble(key = NULL, index = date)

```


### Original Series

```{r}
fish_data_long <- fish_data %>% 
  pivot_longer(cols=2:4,
               names_to = "species",
               values_to = "count") %>% 
  mutate(year=year(date))
   
  
ggplot(data = fish_data_long, aes(x = date, y=count)) +
  geom_line(aes(x = date, y = count)) +  
  scale_x_continuous(breaks = seq(2001, 2011, 1), labels = seq(2001,2011,1)) +
  facet_wrap(~species,
             nrow=3) +
  labs(y = "Number of observations") +
  theme_minimal()

```

**Figure 1.** Time series of coho, jack coho, and steelhead salmon. 

- 2 - 3 bullet points summarizing major patterns / notable trends in the salmon passage time series data
- 


### Seasonplots 

```{r}

```

A finalized seasonplot for each species (coho, jack coho, steelhead) in its own panel. You can either facet_wrap/facet_grid, or use patchwork or cowplot, to make the figure. Add a caption.
Add 2 - 3 bullet points summarizing the major trends you see in the seasonplots.


### Annual Counts

```{r}

```


A finalized figure of annual totals for fish passage, for each of the 3 species (coho, jack coho, steelhead). You decide if this is in a single panel, or multiple panels. Add a figure caption. 
Add 2 - 3 bullet points summarizing major trends you see in the annual totals by species from 2000 - 2010.
